### 2020-10-05 written/software/software_design.tex

\umlclass[x=0, y=-6]{Architecture}{ 
  + arch\_type : string \\ 
  + num\_layers : pos int \\ 
  + post\_affine : bool \\
  }
  { 
  + \_\_call\_\_() \\
  + \_set\_type() \\
  + \_set\_num\_layers() \\
  + \_set\_post\_affine() \\
  + to\_string() \\
  + to\_model() \\
}

\umlclass[x=-1, y=-12]{CouplingArch}{ 
  + D : pos int \\ 
  + num\_couplings : pos int \\
  + num\_units : pos int \\  
  }
  { 
  + \_\_call\_\_() \\
  \# \_set\_D() \\
  \# \_set\_num\_couplings() \\
  \# \_set\_num\_units() \\
  + to\_string() \\
}

\umlclass[x=6, y=-12]{AutoregressiveArch}{ 
  + D : pos int \\ 
  + num\_couplings : pos int \\
  + num\_units : pos int \\  
  }
  { 
  + \_\_call\_\_() \\
  \# \_set\_D() \\
  \# \_set\_num\_ars() \\
  \# \_set\_num\_units() \\
  + to\_string() \\
}

@@

\umlunicompo{Model}{Parameter}
\umlunicompo{Distribution}{Parameter}
\umldep{Model}{Architecture}
\umldep{Model}{Distribution}
\umlinherit{CouplingArch}{Architecture}
\umlinherit{AutoregressiveArch}{Architecture}
\end{umlpackage}

>>>>

\umlclass[x=0, y=-6]{Architecture}{ 
  + arch\_type : string \\ 
  + D : pos int \\ 
  + num\_stages :  int \\ 
  + num\_units :  int \\ 
  + num\_layers :  int \\
  + batch\_norm : bool \\
  + bn\_momentum : float \\ 
  + post\_affine : bool \\
  + bounds : tuple \\
  + random\_seed : int \\
  }
  { 
  \# setters
  + sample(N : int) \\
  + initialize(init\_type, init\_params) \\
  + to\_string() \\
}

@@

\umlunicompo{Model}{Parameter}
\umlunicompo{Distribution}{Parameter}
\umldep{Model}{Architecture}
\umldep{Model}{Distribution}
\end{umlpackage}
